Software Citation Principles

### 2016-02-24 sc-principles/software-citation-principles.tex
add another note

\begin{table}[htbp]
\caption{Use cases for software citation, adapted from \cite{SC-Use-Cases}}
\centering
\scriptsize\setlength{\tabcolsep}{2.5pt}
\begin{tabular}{@{}l l c c c c c c c c@{}}
\toprule
 & & \multicolumn{6}{c}{Requirements} \\
 \cmidrule{3-10}
\multirow{2}{*}{Stakeholder} &	\multirow{2}{*}{Use\slash wants to} 	 &  Software  & \multirow{2}{*}{Author(s)} & \multirow{2}{*}{Version \#} & Release & Location\slash  & \multirow{2}{*}{UID} & Indexed & \multirow{2}{*}{Role} \\
& & name &  &  &  date & repository &  & citations & \\
\midrule
Researcher & someone else's software for a paper	& \textbullet	& \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & & \\
Researcher & someone else's software for new software& \textbullet	& \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & & \\
Researcher & contribute to software 				& \textbullet	& \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & & \textbullet \\
Researcher & find citations of software 			& \textbullet &   &   &   &   & \textbullet & \textbullet & \\
Researcher & credit for software development		& \textbullet & \textbullet &   & \textbullet & \textbullet & \textbullet & & \textbullet \\
Researcher & ``reproduce'' analysis 				& \textbullet &   & \textbullet & \textbullet & \textbullet & \textbullet & & \\
Researcher & benchmark software 					& \textbullet &   & \textbullet & \textbullet & \textbullet & \textbullet & & \\
Researcher & find software to implement task 		& \textbullet & \textbullet &   &   & \textbullet & \textbullet & \textbullet & \\
Publisher & publish software paper					& \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & & \\
Publisher & publish papers that cite software 		& \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \\
Indexer & build catalog of software 				& \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \\
Domain group & build catalog of software 			& \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &  & \\
Library\slash archive & build catalog of software 	& \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &  & \\
Repository & show scientific impact of holdings 	& \textbullet &   &   &   &   & \textbullet & \textbullet & \\
Funder & show how funded software has been used		& \textbullet &   &   &   &   & \textbullet & \textbullet & \\
\bottomrule
\end{tabular}
\label{tab:use_cases}
\end{table}%

>>>>

\begin{table}[htbp]
\caption{Use cases for software citation, adapted from \cite{SC-Use-Cases} \flnote{This table is a little hard to read: it is hard to follow which 'dots' belong to which lines. What about using a alternating (light) background or such to help? Also, I noticed that some entries have the same requirements: maybe they could be combined to one line?}}
\centering
\scriptsize\setlength{\tabcolsep}{2.5pt}
\begin{tabular}{@{}l l c c c c c c c c@{}}
\toprule
 & & \multicolumn{6}{c}{Requirements} \\
 \cmidrule{3-10}
\multirow{2}{*}{Stakeholder} &	\multirow{2}{*}{Use\slash wants to} 	 &  Software  & \multirow{2}{*}{Author(s)} & \multirow{2}{*}{Version \#} & Release & Location\slash  & \multirow{2}{*}{UID} & Indexed & \multirow{2}{*}{Role} \\
& & name &  &  &  date & repository &  & citations & \\
\midrule
Researcher & someone else's software for a paper	& \textbullet	& \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & & \\
Researcher & someone else's software for new software& \textbullet	& \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & & \\
Researcher & contribute to software 				& \textbullet	& \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & & \textbullet \\
Researcher & find citations of software 			& \textbullet &   &   &   &   & \textbullet & \textbullet & \\
Researcher & credit for software development		& \textbullet & \textbullet &   & \textbullet & \textbullet & \textbullet & & \textbullet \\
Researcher & ``reproduce'' analysis 				& \textbullet &   & \textbullet & \textbullet & \textbullet & \textbullet & & \\
Researcher & benchmark software 					& \textbullet &   & \textbullet & \textbullet & \textbullet & \textbullet & & \\
Researcher & find software to implement task 		& \textbullet & \textbullet &   &   & \textbullet & \textbullet & \textbullet & \\
Publisher & publish software paper					& \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & & \\
Publisher & publish papers that cite software 		& \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \\
Indexer & build catalog of software 				& \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \\
Domain group & build catalog of software 			& \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &  & \\
Library\slash archive & build catalog of software 	& \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &  & \\
Repository & show scientific impact of holdings 	& \textbullet &   &   &   &   & \textbullet & \textbullet & \\
Funder & show how funded software has been used		& \textbullet &   &   &   &   & \textbullet & \textbullet & \\
\bottomrule
\end{tabular}
\label{tab:use_cases}
\end{table}%
